Preliminary results

### 2018-07-01 9thJuly/9thJuly.Rmd
day2 added

library(epiDisplay)
library(plyr)
library(tidyverse)

# Number of subjects per survey year
with(NDNS, tab1(SurveyYear, graph = FALSE, decimal = 2))

@@

# noquote(paste(rep("H", 24), 0:23, sep = ""))
#H0  H1  H2  H3  H4  H5  H6  H7  H8  H9  H10 H11 H12 H13 H14 H15 H16 H17 H18 H19 H20 H21 H22 H23
library(poLCA)
f <- cbind(H0, H1, H2, H3, H4, H5, H6, H7, H8, H9, H10,H11,H12,H13,H14,H15,H16,H17,H18,H19,H20,H21,H22,H23) ~ 1
lc3 <- poLCA(f, dta_d1_wide, nclass = 3, graphs = TRUE, maxiter = 10000)

@@

```{r echo=FALSE}
library(kableExtra)
dt <- read.csv("../Tablecsv/Modelfit.csv", header = T)
names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")

kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Model Comparison.") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  row_spec(5, bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; G^2, the likelihood ratio statistic; AIC, Akaike information criterion; BIC, Bayesian information criterion.")
```

@@

>>>>

library(epiDisplay)
library(plyr)
library(tidyverse)
library(poLCA)
# Number of subjects per survey year
with(NDNS, tab1(SurveyYear, graph = FALSE, decimal = 2))

@@

# noquote(paste(rep("H", 24), 0:23, sep = ""))
#H0  H1  H2  H3  H4  H5  H6  H7  H8  H9  H10 H11 H12 H13 H14 H15 H16 H17 H18 H19 H20 H21 H22 H23

f <- cbind(H0, H1, H2, H3, H4, H5, H6, H7, H8, H9, H10,H11,H12,H13,H14,H15,H16,H17,H18,H19,H20,H21,H22,H23) ~ 1
lc3 <- poLCA(f, dta_d1_wide, nclass = 3, graphs = TRUE, maxiter = 10000)

@@

```{r echo=FALSE}
library(kableExtra)
dt <- read.csv("../Tablecsv/Modelfitd01.csv", header = T)
names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")

kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Model Comparison. (Day 1, n = 6153)") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  row_spec(5, bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; G^2, the likelihood ratio statistic; df, degree of freedom; AIC, Akaike information criterion; BIC, Bayesian information criterion.")
```

@@

### day 2 data (Fig.)

library(ggthemr)
lc3 <- poLCA(f, dta_d2_wide, nclass = 3, graphs = FALSE, maxiter = 10000)

a <- (data.frame(lc3$probs))
a$Class <- c("Class1", "Class2", "Class3")

ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 35.92%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  12.50%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 3:  51.58%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))
```

```{r echo=FALSE}
library(kableExtra)
dt <- read.csv("../Tablecsv/Modelfitd02.csv", header = T)
names(dt) <- c("N of classes", "N of parameters", "G^2", "df", "AIC", "BIC", "log-likelihood")

kable(dt, digits = 3, row.names = FALSE, align = "c",
              format = "html", caption = "Model Comparison. (Day 2, n = 6153)") %>%
 kable_styling(font_size = 16, 
        bootstrap_options = c("striped", "hover", "condensed"),
        position = "center", full_width = FALSE) %>% 
  row_spec(5, bold = T, color = "white", background = "#D7261E") %>% 
  footnote(general = "Abbreviation: N, number; G^2, the likelihood ratio statistic; df, degree of freedom; AIC, Akaike information criterion; BIC, Bayesian information criterion.")
```

### Four classes visualisation

# lc4 <- poLCA(f, dta_d2_wide, nclass = 4, graphs = FALSE, maxiter = 10000)
lc5 <- poLCA(f, dta_d2_wide, nclass = 5, graphs = FALSE, maxiter = 10000)

ggplot(a_long[a_long$Class == "Class1", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
  geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 1: 11.80%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class2", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 2:  8.50%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class3", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 3:  25.0%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class4", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) + 
 geom_point(size = 3) + 
  geom_line(size = 1.5) + 
  theme(axis.title = element_text(size = 18), 
        axis.text = element_text(size = 18), 
        axis.line = element_line(colour = "black"), 
        panel.border = element_blank(), 
        panel.background = element_blank(), 
        legend.text = element_text(size = 15), 
        legend.title = element_text(size = 15) 
        # legend.position = "bottom", 
        # legend.direction = "horizontal"
        ) + 
  labs(title = "Class 4:  44.40%", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") + 
  scale_color_discrete(labels = c("Low", "Medium", "High")) + 
  ylim(c(0,1))

ggplot(a_long[a_long$Class == "Class5", ], aes(y = Prob, x=HourN, group = Carbo, color = Carbo)) +
 geom_point(size = 3) +
  geom_line(size = 1.5) +
  theme(axis.title = element_text(size = 18),
        axis.text = element_text(size = 18),
        axis.line = element_line(colour = "black"),
        panel.border = element_blank(),
        panel.background = element_blank(),
        legend.text = element_text(size = 15),
        legend.title = element_text(size = 15)
        # legend.position = "bottom",
        # legend.direction = "horizontal"
        ) +
  labs(title = "Class 5:  %", x = "Hour of the day", y = "Probability",
       color = "Carbohydrate\nintake") +
  scale_color_discrete(labels = c("Low", "Medium", "High")) +
  ylim(c(0,1))
```
